%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Professional Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer (Senior Consultant)} % Job title
    {KPMG Consulting} % Organization
    {\comMadrid, Spain} % Location
    {Jun 2022 – Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Maintain and evolve the main IATA PAY checkout platform, enabling instant payments for airline ticket bookings across different markets and providers.}
        \item {The platform has processed over 1 billion USD in transactions and facilitated the sale of more than 4 million airline tickets successfully.}
        \item {Contribute to the Customer Portal, a web platform for managing payments, refunds, merchants, users, and audits of key actions (e.g., status updates, permission changes).}
        \item {Develop and maintain a payment simulation tool that replicates airline booking flows using various checkout methods: QR, Form, RTP, Script, Iframe, Redirect.}
        \item {Collaborate on the design of RESTful APIs and data models, integrating them into front-end and back-end systems.}
        \item {Lead the migration of multiple Angular applications, resolving legacy issues and improving performance and security (dependency upgrades, CVE resolution).}
        \item {Support stakeholders by providing technical insight for feature planning, implementation, and long-term improvements.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Software Development Intern} % Job title
    {KPMG Consulting} % Organization
    {\comMadrid, Spain} % Location
    {Jan 2022 – Jun 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built an internal web app to simulate test payments and streamline QA flows.}
        \item {Enhanced the quality of backend services by adding unit tests, integration tests, and SonarQube analysis.}
        \item {Gained experience in Agile teams and collaborated in production-grade systems from day one.}
      \end{cvitems}
    }

\end{cventries}
